Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Renamed EBM to CROUGE
Renamed CROUGE to CAROUGE

For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document.

\[ \text{EBM-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]

@@

\[ \text{EBM-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]

>>>>

For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document\footnote{CAROUGE stands for Continuous Abstractive ROUGE. The French word \textbf{carouge} means blackbird}.

\[ \text{CAROUGE-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]

@@

\[ \text{CAROUGE-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
